\documentclass[10pt]{article}
\usepackage{amsmath, amssymb, amsthm, url, hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}
\usepackage[thinc]{esdiff}
\usepackage{commath}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{comment}
\usepackage{pgfplots}

\theoremstyle{plain}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\title{Asymptotic Behavior of the Number of Interval Sums}


\author{Ohto Katila \small \texttt{ohto.katila@gmail.com}}



\let\epsilon\varepsilon

\begin{document}
	\maketitle

	\begin{abstract}
		In this paper we extend the paper of O'Sullivan et al. on interval sums of prime powers to a class of regularly varying functions with index $\alpha>1$, under mild additional assumptions. Let $n_f(x)$ be the length of the largest interval with sum less than $x$ and $S_f(x)$ denote the number of interval sums less than $x$. Our main theorem states that $S_f(x)\sim n_f(x)^2C(\alpha)$, where $C(\alpha)$ is constant dependent only on $\alpha$. This paper applies tools from the theory of regularly varying functions and relates the number of blocks of length $i$ to $\phi(x)=(1+x^{\alpha+1})^{\frac{1}{\alpha+1}}-x$.
	\end{abstract}	
	
	\section{Introduction}
	\textbf{Interval sum} is the sum of consecutive terms in a sequence. Determining the asymptotic behavior of the count of interval sums less than $x$ has been investigated for primes and prime powers \cite{Moser_1963, primePowerConsecutiveSums, primeSquaresConsecutiveSums}. Moser \cite{Moser_1963} determined the asymptotic behavior of interval sums of primes. Tongsomporn et al. \cite{primeSquaresConsecutiveSums} derived strict bounds for the number of interval sums of prime squares. O'Sullivan et al. \cite{primePowerConsecutiveSums} found asymptotic upper and lower bounds for the number of interval sums of prime powers. 
	
	To the best of our knowledge, no asymptotic formula is known for more general sequences. An asymptotic formula is found for the number of interval sums for a class of sequences $\left(f(i)\right)_{i=1}^{\infty}$, where $f$ is measurable, locally bounded away from 0 and $\infty$, eventually increasing, and regularly varying with index $\alpha> 1$. This generalizes and extends O'Sullivan et al.'s work and provides exact asymptotics for the number of interval sums of prime powers. 
	
	Our main theorem provides an asymptotic for the interval sum counting function
	\begin{equation}
	S_f(x)=\#\left\{(i, j)\in\mathbb{N}^2\mid i\le j, f(i)+f(i+1)+\dots+f(j)\le x\right\}.
	\end{equation}
	That is
	\begin{equation}
	S_f(x)\sim n^2C(\alpha) \qquad n=n_f(x)\to\infty
	\end{equation}
	where n is the length of the largest interval, with following asymptotic relation to $x$, $x\sim \frac{nf(n)}{\alpha+1}, x\to\infty$ and 
	\begin{equation}
	C(\alpha)=\frac{1}{2(\alpha+1)}
	\frac{\Gamma(\frac{1}{\alpha+1})\Gamma(\frac{\alpha-1}{\alpha+1})}{\Gamma(\frac{\alpha}{\alpha+1})}.
	\end{equation} 
	
	The proof relies on classical results from the theory of regular variation, in particular the uniform convergence theorem and Potter's bound \cite{bingham1987regular}. The function $S_f(x)$ can be split into a sum of $s_{i, f}$ that counts the number of intervals of length $i$. The main idea in the proof is that $s_{i, f}$ can be related to the inverse of 
	\begin{equation}
	\phi(x)=(1+x^{\alpha+1})^{\frac{1}{\alpha+1}}-x
	\end{equation} 
	which allows us to calculate the exact coefficient in the asymptotic.
	
	
	This paper is organized as follows. Section \ref{notation} defines our notation. Section \ref{preliminaries} first proves basic lemma about asymptotics, then a lemma that relates $\phi$ and $s_{i, f}$, and finally a lemma that calculates the integral of the inverse of $\phi$. Section \ref{mainTheorem} proves the main theorem \ref{BlockSumsforAlphaGr1} and one technical lemma bounding the sum of $s_{i, f}$ for small $i$.
	
	\section{Notation}\label{notation}
	\begin{itemize}
		\item The function $f\colon\left[ 0, \infty\right)\to \left[0, \infty\right)$ is assumed to satisfy following criterion: measurable, eventually increasing, locally bounded away from $0$ and $\infty$, and regularly varying with index $\alpha$ (see definition~\ref{RV_def} or \cite{bingham1987regular}).
		\item $S_f(x)=\#\left\{(i, j)\in\mathbb{N}^2\mid i\le j, f(i)+f(i+1)+\dots+f(j)\le x\right\}$ – the number of interval sums below $x$.
		\item $s_{k, f}(x)=\#\left\{(i, j)\in\mathbb{N}^2\mid j-i=k-1, f(i)+f(i+1)+\dots+f(j)\le x\right\}$ – the number of 	interval sums of length $k$ below $x$.
		\item $f(x)\sim g(x),\ x\to a$ – meaning $\lim_{x\to a} \frac{f(x)}{g(x)} = 1$.
		The part "$x\to a$" is often omitted when it is clear from context.
		\item $f(x)\lesssim g(x)$ – meaning $\limsup\frac{f(x)}{g(x)}\le1$.
		\item $f(x)\gtrsim g(x)$ – meaning $g(x)\lesssim f(x)$.
		\item sums of the form $\displaystyle\sum_{i=x}^{y} F(i)$ are denoted with $\displaystyle\sum_{x\le i< y} F(i)$.
		\item $f(x)=O(g(x))$ – there exists $C>0$ such that $\abs{f(x)}\le Cg(x)$ for all sufficiently large $x$.
		\item $f(x)=o(g(x))$ – shorthand for
		\[
		\lim_{x\to\infty} \frac{f(x)}{g(x)}=0
		\]
		\item Define $n:=n_f(x)$, where 
		\begin{equation}
			n_f(x)=\max\left\{n\in \mathbb{N} \mid \sum_{i=1}^{n} f(i)\leq x\right\}
		\end{equation}
		that is, length of the largest interval.
	\end{itemize}
	\section{Preliminaries}\label{preliminaries}
	
	\begin{definition}\label{RV_def}
		Function $f\colon\left[ 0, \infty \right)\to\left[0, \infty \right)$ is \textbf{regularly varying} with \textbf{index} $\alpha$ if for all $\lambda>0$
		\begin{equation}
			\lim_{x\to\infty}\frac{f(\lambda x)}{f(x)}=\lambda^\alpha.
		\end{equation}
	\end{definition}
	
	\begin{definition}\label{SV_def}
		Function $L\colon\left[ 0, \infty \right)\to\left[ 0, \infty \right)$ is \textbf{slowly varying} if for all $\lambda>0$
		\begin{equation}
			\lim_{x\to\infty}\frac{L(\lambda x)}{L(x)}=1.	
		\end{equation}
	\end{definition}
	

	
	Since $f$ is measurable and regularly varying with index $\alpha$, we have $f(x)=x^\alpha L(x)$, for slowly varying $L$ (see Theorem 1.4.1 in \cite{bingham1987regular}).
	
	\begin{lemma}\label{sum f Asymp}
		We have
		\begin{equation}
		x\sim \frac{n^{\alpha+1}L(n)}{\alpha+1}=\frac{nf(n)}{\alpha+1}
		\end{equation}
		for $\alpha>-1$.
	\end{lemma}
	\begin{proof}
		This is a direct consequence of Karamata's theorem (see proposition 1.5.8 in \cite{bingham1987regular} or Proposition~\ref{karamata} in the appendix).
	\end{proof}
	
	\begin{lemma}\label{s asymp}
		Let $\epsilon>0$ and $\lambda\geq\epsilon$, then $s_{\lambda n, f}(x)$ has the following asymptotic
		\begin{equation}
			s_{\lambda n, f}(x)\sim n\phi^{-1}\left(\lambda\right)
		\end{equation}
		where $\phi(x)=(1+x^{\alpha+1})^{\frac{1}{\alpha+1}}-x$.
	\end{lemma}
	
	\begin{proof}
		Let $l,k>0$ be such that $k-l=\lambda$ and $k^{\alpha+1}-l^{\alpha+1}=1$. Since $n$ is the length of the largest interval, $\lambda<1$. Since $\lambda<1$, it follows that such $k$ and $l$ exists, by monotonicity of $(l+\lambda)^{\alpha+1}-l^{\alpha+1}$. Now Using mean-value theorem we get that for some $\zeta\in(l, k)$
		\begin{equation}
			1=(l+\lambda)^{\alpha+1}-l^{\alpha+1}=(\alpha+1)\zeta^\alpha\lambda>(\alpha+1)l^\alpha\epsilon.
		\end{equation}
		Thus
		\begin{align}
			l<\left(\frac{1}{(\alpha+1)\epsilon}\right)^{\frac{1}{\alpha}}.
		\end{align}
		It follows that $l$ and $k$ are bounded above. Now we can use the uniform convergence theorem (see Theorem 1.2.1 in \cite{bingham1987regular} or Theorem~\ref{UCT} in the Appendix) and lemma~\ref{sum f Asymp}
		\begin{align}
			x\sim\frac{1}{\alpha+1}L(n)n^{\alpha+1}&=\\
			\frac{1}{\alpha+1}L(n)n^{\alpha+1}(k^{\alpha+1}-l^{\alpha+1})&=\\
			L(n)\int_{nl}^{nk} t^\alpha dt&\sim\\
			L(n)\sum_{i=nl}^{nk} i^\alpha&=\\
			\sum_{i=nl}^{nk} i^\alpha L(n) &\sim \sum_{i=nl}^{nk} f(i).
		\end{align}
		It follows that 
		\begin{equation}\label{x sim nk-nl sum}
			x\sim \sum_{i=nl}^{nk} f(i).
		\end{equation}
		Using $k^{\alpha+1}-l^{\alpha+1}=1$ we get
		\begin{align}
			k^{\alpha+1}-l^{\alpha+1}&= 1\\
			k-l&= (1+l^{\alpha+1})^{\frac{1}{\alpha+1}}-l\\
			\lambda&= (1+l^{\alpha+1})^{\frac{1}{\alpha+1}}-l\\
			ln&= n\phi^{-1}(\lambda).\label{ln eq}
		\end{align}
		Lemma \ref{phi integral} proves that $\phi^{-1}$ is well defined. Since $s_{\lambda n, f}(x)$ counts the number of intervals of length $\lambda n$, we get from equations~\ref{x sim nk-nl sum} and~\ref{ln eq}
		\begin{equation}
			s_{\lambda n, f}(x) \sim nl = n\phi^{-1}(\lambda).
		\end{equation}
	\end{proof}
	
	\begin{lemma}\label{phi integral}
		The function $\phi:(0,\infty)\to(0,1)$, $\phi(x)=(1+x^{\alpha+1})^{\frac{1}{\alpha+1}}-x$ is a strictly decreasing bijection, has an inverse, and
		\begin{equation}
		\int_{0}^{1} \phi^{-1}(t)dt=\frac{1}{2(\alpha+1)}
		\frac{\Gamma(\frac{1}{\alpha+1})\Gamma(\frac{\alpha-1}{\alpha+1})}{\Gamma(\frac{\alpha}{\alpha+1})}
		\end{equation}
		for $\alpha>1$.
	\end{lemma}
	
	\begin{proof}
		It is straightforward to verify that $\phi$ has an inverse and it's integral converges. Doing change of variables and using analytic continuation of the beta function, gives the evaluation. For full details see the appendix \ref{appendix:phi-integral}.
	\end{proof}
	
	\section{Proof of the Main Theorem}\label{mainTheorem}
	\begin{lemma}\label{head's neglible}
		Let $\epsilon>0$ and $\alpha>1$, then 
		\begin{equation}
		\sum_{i=1}^{n\epsilon} s_{i, f}(x)=O(n^2)\epsilon^{\frac{1}{2}(1-\frac{1}{\alpha})},
		\end{equation}
		where the $O(n^2)$ term is independent of $\epsilon$.
	\end{lemma}
	
	\begin{proof}
		Since
		\begin{align}
			x\ge f(i)+\dots+f(i+k-1)&\ge kf(i)\\
			f^{-1}\left(\frac{x}{k}\right)&\ge i,
		\end{align}	 
		it follows that $s_{k, f}(x)\le f^{-1}\left(\frac{x}{k}\right)$. The inverse of a regularly varying function is regularly varying with index $\frac{1}{\alpha}$ (see Theorem 1.5.12 of \cite{bingham1987regular} or Theorem~\ref{RVinverse} in the Appendix). Let $f^{-1}(x)=x^{\frac{1}{\alpha}}\tilde{L}(x)$. We get
		\begin{equation}
		\sum_{i=1}^{n\epsilon} f^{-1}\left(\frac{x}{i}\right)\sim \int_{1}^{n\epsilon} f^{-1}\left(\frac{x}{t}\right)dt=x^{\frac{1}{\alpha}}\int_{1}^{n\epsilon} t^{-\frac{1}{\alpha}}\tilde{L}\left(\frac{x}{t}\right)dt.
		\end{equation}
		By Potter's bound (ii)
		\begin{equation}
		\tilde{L}\left(\frac{x}{t}\right)\le M\tilde{L}\left(\frac{x}{n}\right)\left(\frac{n}{t}\right)^{\delta},
		\end{equation}
		where $M$ is the constant from Potter's bound and $\delta=\frac{1}{2}(1-\frac{1}{\alpha})$. Now we can bound the integral
		\begin{align}
			x^{\frac{1}{\alpha}}\int_{1}^{n\epsilon} t^{-\frac{1}{\alpha}}\tilde{L}\left(\frac{x}{t}\right)dt&\le
			x^{\frac{1}{\alpha}}M\tilde{L}\left(\frac{x}{n}\right)n^\delta\int_{1}^{n\epsilon} t^{-\frac{1}{\alpha}-\delta}.
		\end{align}
		By definition
		\begin{align}
			f^{-1}(f(n))&\sim n\\
			n\tilde{L}(n^\alpha L(n))L(n)^{1/\alpha}&\sim n\\
			\tilde{L}(n^\alpha L(n))L(n)^{1/\alpha}&\sim 1. \label{L eq sim 1}
		\end{align}
		Using the relation between $x$ and $n$ obtained in Lemma~\ref{sum f Asymp}
		\begin{equation}
			\tilde{L}\left(\frac{x}{n}\right)\sim \tilde{L}\left(n^\alpha L(n)\right).\label{triv L thing}
		\end{equation}
		Thus, from equations \ref{triv L thing} and \ref{L eq sim 1}
		\begin{align}
			x^{\frac{1}{\alpha}}M\tilde{L}\left(\frac{x}{n}\right)n^\delta\int_{1}^{n\epsilon} t^{-\frac{1}{\alpha}-\delta}
			&\sim Mn^{2}L(n)^{\frac{1}{\alpha}}\tilde{L}(n^\alpha L(n))\frac{2\alpha}{\alpha-1}\epsilon^{\frac{1}{2}(1-\frac{1}{\alpha})}\\
			&=O(n^2)\epsilon^{\frac{1}{2}(1-\frac{1}{\alpha})}.
		\end{align}		
	\end{proof}
	
	\begin{theorem}\label{BlockSumsforAlphaGr1}
		Under the assumptions and notation in \ref{notation}, the function $S_f(x)$ has the asymptotic $n^2 C(\alpha)$ for $\alpha>1$, where 
		\begin{equation}
			C(\alpha)=\frac{1}{2(\alpha+1)}
			\frac{\Gamma(\frac{1}{\alpha+1})\Gamma(\frac{\alpha-1}{\alpha+1})}{\Gamma(\frac{\alpha}{\alpha+1})}.
		\end{equation}
	\end{theorem}
	
	\begin{proof}
		Let $\epsilon>0$. From the definition of $S$ and $s_{i, f}$ it follows that
		\begin{equation}
		S_f(x)=\sum_{i=1}^{n} s_{i, f}(x).
		\end{equation}
		Splitting the sum
		\begin{equation}\label{sumSplit}
		S_f(x)=\sum_{i=1}^{n\epsilon} s_{i, f}(x)+\sum_{i=n\epsilon}^{n} s_{i, f}(x).
		\end{equation}
		Using Lemma~\ref{s asymp} and monotonicity of $\phi^{-1}$, we get
		\begin{align}
			\sum_{i=n\epsilon}^{n} s_{i, f}(x)&\sim \sum_{i=n\epsilon}^{n} n\phi^{-1}\left(\frac{i}{n}\right)\\
			&=n\sum_{i=n\epsilon}^{n} \phi^{-1}\left(\frac{i}{n}\right)\\
			&\sim n \int_{n\epsilon}^{n} \phi^{-1}\left(\frac{t}{n}\right)dt\\
			&=n^2\int_{\epsilon}^{1} \phi^{-1}(t)dt.
		\end{align}
		Since the integral converges
		\begin{equation}
			\lim_{\epsilon\to0^+} \int_{\epsilon}^{1} \phi^{-1}(t)dt =\int_{0}^{1} \phi^{-1}(t)dt
		\end{equation}
		From Lemma~\ref{head's neglible}, it follows that the first sum in \ref{sumSplit} is negligible in the asymptotic, hence taking $\epsilon\to 0$ finishes the proof. 
	\end{proof}
	
	\begin{corollary}
		The number of interval sums for $f(x)=x^\alpha, \alpha>1$ is asymptotic to
		\begin{equation}
			x^{\frac{2}{1+\alpha}}(\alpha+1)^{\frac{2}{1+\alpha}}C(\alpha)
		\end{equation}
	\end{corollary}
	\begin{proof}
		From theorem~\ref{BlockSumsforAlphaGr1} and inverting lemma~\ref{sum f Asymp}, it follows that
		\begin{equation}
			S_f(x)\sim n^2C(\alpha)\sim ((\alpha+1)^{\frac{1}{1+\alpha}}x^{\frac{1}{1+\alpha}})^2C(\alpha)\sim x^{\frac{2}{1+\alpha}}(\alpha+1)^{\frac{2}{1+\alpha}}C(\alpha)
		\end{equation}
	\end{proof}
	
	\begin{corollary}
		Number of interval sums for prime powers $p^\alpha, \alpha>1$ is asymptotic to
		\begin{equation}
			(1+\alpha)^2 C(\alpha)\left(\frac{x}{\log(x)^\alpha}\right)^{\frac{2}{\alpha+1}}
		\end{equation}
	\end{corollary}
	\begin{proof}
		From the prime number theorem, it follows that $f(x)\sim(x\log (x))^\alpha$. Now using lemma~\ref{sum f Asymp} it follows that $x\sim \frac{1}{\alpha+1}n^{\alpha+1}\log^\alpha(n)$. It is easy to see that $n=(1+\alpha)\left(\frac{x}{\log^{\alpha}(x)}\right)^{\frac{1}{1+\alpha}}$ is the asymptotic inverse. By theorem~\ref{BlockSumsforAlphaGr1} the corollary follows.
	\end{proof}
	
	
	\section{Convergence of the Asymptotic Formula}
	
	Figures~\ref{SVeffectsOnConvergence} and \ref{indexEffectsOnConvergence} show the impact of the slowly varying part and the index on convergence, respectively. We can observe that increasing the index slows down the convergence, and a larger absolute value in growth rate in the slowly varying part seem to corresponds to slower convergence.
	
	See the table \ref{exampleRelErrors} below for relative error of the asymptotic at $x=10^{20}$ for varying functions.
	\begin{table}[H]
	\centering
	\begin{tabular}{ |l|l| }
		\toprule
		$f(x)$ & relative error at $x=10^{20}$ \\ 
		\midrule
		%$x^2$ & $\num[round-mode=places, round-precision=3]{0.03706192}\%$ \\ 
		$x^3$ & $\num[round-mode=places, round-precision=3]{0.0450621036211}\%$ \\ 
		%$x^4$ & $\num[round-mode=places, round-precision=3]{0.19448766}\%$ \\ 
		%$x^5$ & $\num[round-mode=places, round-precision=3]{0.771010584994}\%$ \\ 
		$x^3 \log(x)$ & $\num[round-mode=places, round-precision=3]{1.43313232124}\%$ \\ 
		$x^3\log(x)^2$ & $\num[round-mode=places, round-precision=3]{2.83630518218}\%$ \\ 
		%$x^4/\sqrt{\log(x)}$ & $\num[round-mode=places, round-precision=3]{0.214554815854}\%$ \\
		$x^4/\log(x)$ & $\num[round-mode=places, round-precision=3]{0.622234950826}\%$ \\
		\bottomrule
	\end{tabular}
	\caption{Relative error of the asymptotic at $x=10^{20}$ for various functions.}
	\label{exampleRelErrors}
	\end{table}
	
	These findings align with our analysis: the proofs rely on the uniform convergence theorem, which gives slower convergence for larger growth rates, and the convergence of the sum to integral is slower for larger indices.
	
	\section{Conclusion}
	The main theorem gives an asymptotic for the number of interval sums below $x$, namely $S_f(x)\sim n^2 C(\alpha)$. It remains an open question what happens in the case $\alpha\le 1$; our methods can't handle that case since the integral in Lemma~\ref{phi integral} diverges. Future work could therefore investigate the case $\alpha\le 1$, it seems fruitful to use methods of de Haan theory to investigate the case $\alpha=1$.
	
\appendix
\setcounter{theorem}{0}
\setcounter{lemma}{0}
\setcounter{proposition}{0}
\setcounter{definition}{0}
\renewcommand{\thetheorem}{\Alph{section}.\arabic{theorem}}
\renewcommand{\thelemma}{\Alph{section}.\arabic{lemma}}
\renewcommand{\theproposition}{\Alph{section}.\arabic{proposition}}
\renewcommand{\thedefinition}{\Alph{section}.\arabic{definition}}
\section{Appendix: The Integral Of The Function Phi}\label{appendix:phi-integral}
Here we give detailed evaluation of the integral of $\phi$.
\begin{proof}
	Taking the derivative of $\phi$
	\begin{align}
		\diff{\phi}{x}&=(1+x^{\alpha+1})^{-\frac{\alpha}{\alpha+1}}x^{\alpha}-1<0
	\end{align}
	As $\phi(0)=1$ and $\lim_{x\to\infty}\phi(x)=0$, $\phi$ is a bijection, hence it has an inverse. Since $\phi$ is a strictly decreasing bijection
	\begin{equation}
		\int_{0}^{1} \phi^{-1}(x)dx=\int_{0}^{\infty} \phi(x)dx.
	\end{equation}
	The integral converges as
	\begin{equation}
		\phi(x)=(1+x^{\alpha+1})^{\frac{1}{\alpha+1}}-x<\frac{1}{1+\alpha}x^{-\alpha}.
	\end{equation}
	
	Doing a change of variables $t=\frac{x^{\alpha+1}}{1+x^{\alpha+1}}$, $x=(\frac{t}{1-t})^{\frac{1}{\alpha+1}}$, we get
	\begin{align}
		\int_{0}^{\infty} \phi(x)dx&=\int_{0}^{1} (1-t)^{-\frac{1}{\alpha+1}}(1-t^{\frac{1}{\alpha+1}})
		\frac{1}{\alpha+1}\left(\frac{t}{1-t}\right)^{-\frac{\alpha}{\alpha+1}}(1-t)^{-2}dt\\
		&=\frac{1}{\alpha+1}\int_{0}^{1} (1-t)^{-\frac{2}{\alpha+1}-1}
		(t^{-\frac{\alpha}{\alpha+1}}-t^{\frac{1-\alpha}{\alpha+1}})dt.
	\end{align}
	
	Let $g_r(t)=(1-t)^{r-\frac{2}{\alpha+1}-1}
	(t^{-\frac{\alpha}{\alpha+1}}-t^{\frac{1-\alpha}{\alpha+1}})$ and $g(t)=(1-t)^{-\frac{2}{\alpha+1}-1}
	(t^{-\frac{\alpha}{\alpha+1}}-t^{\frac{1-\alpha}{\alpha+1}})$. Since for each $r>0$, $g_r(t)\to g(t), r\to0$ pointwise
	and $\abs{g_r(t)}<\abs{g(t)}$, we can use the dominated convergence theorem. Thus
	\begin{equation}
		\int_{0}^{1} (1-t)^{-\frac{2}{\alpha+1}-1}
		(t^{-\frac{\alpha}{\alpha+1}}-t^{\frac{1-\alpha}{\alpha+1}})dt
		=\lim_{r\to0^+} \int_{0}^{1} (1-t)^{r-\frac{2}{\alpha+1}-1}
		(t^{-\frac{\alpha}{\alpha+1}}-t^{\frac{1-\alpha}{\alpha+1}})dt.
	\end{equation}
	Let $B$ be the beta function (see NIST DLMF § 5.12.1 \cite{NIST:DLMF})
	\begin{align}
		B(z_1, z_2)=\int_{0}^{1} t^{z_1-1}(1-t)^{z_2-1}dt=\frac{\Gamma(z_1)\Gamma(z_2)}{\Gamma(z_1+z_2)}.
	\end{align}
	The beta function can be analytically extended using Pochhammer's integral (see NIST DLMF § 5.12.12 \cite{NIST:DLMF}).
	\begin{align}
		\int_{0}^{\infty} \phi(x)dx&=\frac{1}{\alpha+1}\int_{0}^{1} (1-t)^{-\frac{2}{\alpha+1}-1}
		(t^{-\frac{\alpha}{\alpha+1}}-t^{\frac{1-\alpha}{\alpha+1}})dt\\
		&=\frac{1}{\alpha+1} \lim_{r\to0^+} \int_{0}^{1} (1-t)^{r-\frac{2}{\alpha+1}-1}
		(t^{-\frac{\alpha}{\alpha+1}}-t^{\frac{1-\alpha}{\alpha+1}})dt\\
		&=\frac{1}{\alpha+1}\lim_{r\to 0^+}\left(B\left(\frac{1}{\alpha+1}, r-\frac{2}{\alpha+1}\right)-
		B\left(\frac{2}{\alpha+1}, r-\frac{2}{\alpha+1}\right)\right).
	\end{align}
	Using the gamma expression for beta functions, we get
	\begin{align}
		\int_{0}^{\infty} \phi(x)dx&=\frac{1}{\alpha+1}\lim_{r\to 0^+}\left(
		\frac{\Gamma(\frac{1}{\alpha+1})\Gamma(r-\frac{2}{\alpha+1})}{\Gamma(\frac{1}{\alpha+1}+r-\frac{2}{\alpha+1})}
		-
		\frac{\Gamma(\frac{2}{\alpha+1})\Gamma(r-\frac{2}{\alpha+1})}{\Gamma(\frac{2}{\alpha+1}+r-\frac{2}{\alpha+1})}
		\right)\\
		&=\frac{1}{\alpha+1}\lim_{r\to 0^+}\left(
		\frac{\Gamma(\frac{1}{\alpha+1})\Gamma(-\frac{2}{\alpha+1})}{\Gamma(-\frac{1}{\alpha+1})}
		-
		\frac{\Gamma(\frac{2}{\alpha+1})\Gamma(-\frac{2}{\alpha+1})}{\Gamma(r)}
		\right).
	\end{align}
	Since $\Gamma(t)=\frac{\Gamma(1+t)}{t}$, we have $\Gamma(t)\sim\frac{1}{t}, \ t\to 0$. Thus
	\begin{equation}
		\lim_{r\to 0}\frac{\Gamma(\frac{2}{\alpha+1})\Gamma(-\frac{2}{\alpha+1})}{\Gamma(r)}=0
	\end{equation}
	so the expression simplifies to
	\begin{align}
		\int_{0}^{\infty} \phi(x)dx&=\frac{1}{\alpha+1}
		\frac{\Gamma(\frac{1}{\alpha+1})\Gamma(-\frac{2}{\alpha+1})}{\Gamma(-\frac{1}{\alpha+1})}
		\\
		&=\frac{1}{2(\alpha+1)}
		\frac{\Gamma(\frac{1}{\alpha+1})\Gamma(\frac{\alpha-1}{\alpha+1})}{\Gamma(\frac{\alpha}{\alpha+1})}
	\end{align}
	where the last equality follows from $z\Gamma(z)=\Gamma(z+1)$.
\end{proof}
\setcounter{theorem}{0}
\setcounter{lemma}{0}
\setcounter{proposition}{0}
\setcounter{definition}{0}
\section{Appendix: Selected Results on Regular Variation}

For convenience, we reproduce several standard theorems from
\cite{bingham1987regular} we assume through this section that $f$ and $l$ are measurable.

\begin{theorem}[Uniform Convergence Theorem]\label{UCT}
	If $l$ is slowly varying then
	\[
	\frac{l(\lambda x)}{l(x)}\to 1\qquad (x\to \infty)
	\]
	uniformly in each compact $\lambda\text{-set}$ in $(0, \infty)$.
\end{theorem}
\begin{proof}
	See Theorem 1.2.1 in \cite{bingham1987regular}.
\end{proof}

\begin{theorem}[Potters Theorem]\label{PottersBound}
	\begin{enumerate}[label=(\roman*)]
		\item If $l$ is slowly varying function then for any chosen constants $A>1$, $\delta>0$ there exists $X=X(A, \delta)$ such that
		\[
		\frac{l(y)}{l(x)}\le A\max\left\{\left(\frac{y}{x}\right)^{\delta}, \left(\frac{x}{y}\right)^{\delta}\right\} \qquad (x\ge X, y\ge X)
		\]
		
		\item If further, $l$ is bounded away from $0$ and $\infty$ in every compact subset of $[0, \infty)$, then for every $\delta>0$ there exists $A'=A'(\delta)>1$ such that
		\[
		\frac{l(y)}{l(x)}\le A'\max\left\{\left(\frac{y}{x}\right)^{\delta}, \left(\frac{x}{y}\right)^{\delta}\right\} \qquad (x\ge 0, y\ge 0)
		\]
		
		\item If $f$ is regularly varying of index $\rho$ then for any chosen $A>1$, $\delta>0$ there exists $X=X(A, \delta)$ such that 
		\[
		\frac{f(y)}{f(x)}\le A\max\left\{\left(\frac{y}{x}\right)^{\rho+\delta}, \left(\frac{x}{y}\right)^{\rho+\delta}\right\} \qquad (x\ge X, y\ge X)
		\]
	\end{enumerate}
\end{theorem}
\begin{proof}
	See Theorem 1.5.6 in \cite{bingham1987regular}.
\end{proof}

\begin{proposition}[Karamata's Theorem]\label{karamata}
	If $l$ is slowly varying, X is so large that $l(x)$ is locally bounded in $[X, \infty)$, and $\alpha>-1$, then
	\[
	\int_{X}^{x} t^\alpha l(t)dt\sim \frac{x^{\alpha+1}l(x)}{\alpha+1}\qquad (x\to\infty)
	\]
\end{proposition}
\begin{proof}
	See Proposition 1.5.8 in \cite{bingham1987regular}.
\end{proof}

\begin{definition}[Generalized inverse]
	Generalized inverse of $f$ is defined by
	\begin{align}
		f^{\leftarrow}(x)=\inf\left\{x\mid f(x)=y\right\}
	\end{align}
\end{definition}

\begin{theorem}\label{RVinverse}
	If $f\in RV_\alpha$ with $\alpha>0$, there exits $g\in RV_{\frac{1}{\alpha}}$ with 
	\[
	f(g(x))\sim g(f(x))\sim x\qquad (x\to \infty).
	\]
	Here $g$ (an asymptotic inverse of $f$) is determined uniquely to within asymptotic equivalence, and one version of g is $f^{\leftarrow}$.
\end{theorem}
\begin{proof}
	See theorem 1.5.12 in \cite{bingham1987regular}.
\end{proof}

\section*{Figures on convergence}
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\begin{axis}
			[
			label style = { font = \LARGE },
			ymode=normal,
			axis lines=left,
			xlabel=$\log_{10}(x)$,
			ylabel=$\frac{S(x)}{n^2}$,
			ymin=0,
			ymax=1,
			legend pos=south east,
			]
			\addplot[red, thick, domain=5:20] {0.655514388573};
			\addlegendentry{$C(3)$}
			\addplot[smooth, thick] table{
				5 	 0.279586
				6 	 0.404537
				7 	 0.498704
				8 	 0.566753
				9 	 0.602608
				10	 0.622818
				11	 0.63592
				12	 0.643569
				13	 0.648045
				14	 0.65099
				15	 0.652635
				16	 0.653749
				17	 0.654374
				18	 0.654807
				19 	 0.655054
				20	 0.655219
			};
			\addlegendentry{$f(x)=x^3$}
			\addplot[smooth, dashed, thick] table{
				5 0.181406
				6 0.333045
				7 0.436385
				8 0.51158
				9 0.562007
				10 0.591895
				11 0.610496
				12 0.623089
				13 0.631517
				14 0.636507
				15 0.639613
				16 0.641916
				17 0.643398
				18 0.64458
				19 0.645429
				20 0.64612
			};
			\addlegendentry{$f(x)=x^3\log(x)$}
			\addplot[smooth, dotted, thick] table{
				5 0.114187
				6 0.245542
				7 0.375879
				8 0.452546
				9 0.518537
				10 0.558425
				11 0.584521
				12 0.603029
				13 0.613707
				14 0.620829
				15 0.626311
				16 0.629712
				17 0.632283
				18 0.634184
				19 0.635672
				20 0.636922	
			};
			\addlegendentry{$f(x)=x^3\log^2(x)$}
		\end{axis}
		
	\end{tikzpicture}
	\caption{Example of how the slowly varying part affects convergence}
	\label{SVeffectsOnConvergence}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\begin{axis}
			[
			label style = { font = \LARGE },
			ymode=normal,
			axis lines=left,
			xlabel=$\log_{10}(x)$,
			ylabel=$\frac{S(x)}{C(\alpha)n^2}$,
			ymin=0,
			ymax=1,
			legend pos=south east,
			]
			\addplot[red, thick, domain=5:20] {1};
			\addlegendentry{$1$}
			\addplot[smooth, thick] table{
				5 0.7190649474
				6 0.8432680421
				7 0.9062543204
				8 0.9463711807
				9 0.9668099942
				10 0.9791124528
				11 0.9866137034
				12 0.991276796
				13 0.9942134461
				14 0.9961380048
				15 0.997401421
				16 0.9982504911
				17 0.9988154056
				18 0.999195789
				19 0.9994539063
				20 0.9996293808
			};
			\addlegendentry{$f(x)=x^2$}
			\addplot[smooth, dashed, thick] table{
				5 0.4265139025
				6 0.6171290929
				7 0.7607826902
				8 0.8645927685
				9 0.9192902711
				10 0.9501210208
				11 0.9701083776
				12 0.9817770765
				13 0.9886053019
				14 0.9930979569
				15 0.9956074365
				16 0.9973068653
				17 0.998260315
				18 0.9989208649
				19 0.9992976682
				20 0.999549379
			};
			\addlegendentry{$f(x)=x^3$}
			\addplot[smooth, dotted, thick] table{
				5 0.1286654854
				6 0.3315713285
				7 0.5190241531
				8 0.6722635208
				9 0.7841729099
				10 0.8569712311
				11 0.9049426154
				12 0.9377017748
				13 0.9614184049
				14 0.9736709469
				15 0.9830932284
				16 0.9889955649
				17 0.9928220363
				18 0.99533385
				19 0.9968852143
				20 0.9980551234
			};
			\addlegendentry{$f(x)=x^4$}
		\end{axis}
		
	\end{tikzpicture}
	\caption{Example of how the index affects convergence}
	\label{indexEffectsOnConvergence}
\end{figure}

	
	\bibliographystyle{plain}
	\bibliography{references}
\end{document}